The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-31 cordillera-climate.tex
Add some sentences on precipitation changes

Our representation of climate history by constant temperature offsets is voluntarily simplistic. To better understand the transient character of the LGM Cordilleran ice sheet, time-dependent palaeo-climate forcing would be needed. Although it is clear that past temperature changes over the region were neither homogeneous nor constant in time, and probably associated with precipitation changes, their patterns are not trivial and may potentially display a~strong inter-dependence with the evolution of the Cordilleran and Laurentide ice sheets. A~more correct, yet more complex approach would be to use coupling to a~GCM of intermediate complexity \citep{yoshimori-etal-2001,calov-etal-2002,abeouchi-etal-2007,charbit-etal-2013}.

>>>>

Our representation of climate history by constant temperature offsets is voluntarily simplistic. To better understand the transient character of the LGM Cordilleran ice sheet, time-dependent palaeo-climate forcing would be needed. Although it is clear that past temperature changes over the region were neither homogeneous nor constant in time, their patterns are not trivial and may potentially display a~strong inter-dependence with the evolution of the Cordilleran and Laurentide ice sheets. As previously discussed, potential effects of the growing ice-sheet on precipitation changes are not included in our model. Although the ice sheet interior likely became dryer, precipitation may increased along part of the margin where the presence of ice imposed ascending winds. In this context, using a~GCM of intermediate complexity \citep{yoshimori-etal-2001,calov-etal-2002,abeouchi-etal-2007,charbit-etal-2013} may help producing more westerly-centred ice configurations than those presented here (Fig.~\ref{fig:best}).
